J-ReCoVer: Java Reducer Commutativity Verifier

### 2018-11-05 draft.tex
Update exp graphes and tables

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{color}
\usepackage{alltt}
\usepackage{xspace}
\usepackage{multirow}
\pagestyle{plain}
\usepackage{xcolor}
\usepackage{algorithm2e}
\usepackage{tikz}
\usepackage{etoolbox}
\usepackage{mathtools}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{listings}
%\usepackage{adjustbox}
%\usetikzlibrary{arrows,calc}
\captionsetup{compatibility=false}
%\usepackage{a4wide}
%\usepackage[margin=40mm, top=35mm]{geometry}

@@

\begin{table}
	\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
							   & \small CBMC\cite{cbmc2} 	& \small CPA-Seq\cite{cpachecker} & \small  ESBMC-kind\cite{esbmc} & \small  UAutomizer\cite{uautomizer} &\small  VeriAbs\cite{veriabs} &\small J-Recover\\
\hline
\hline
\small \textsf{rangesum}	& 0.96 	   & 30 		 & 2.2 				 &  10				 & 180       &6.1\\
\hline
\small \textsf{avg}			 &  TO      &  TO		  &  TO				 &  TO				 &  2          &5.2\\
\hline
\small \textsf{max}		    &  TO      &  TO		 &  TO				& TO				 &  7         &5.8\\
\hline
\small \textsf{sep}		     &  TO      &  TO		  &  TO				 & TO				 &  TO        &6.3\\
\hline
\small \textsf{sum}		    &  TO      &  TO		 &  TO				& TO				&  1.7       &5.3\\
\hline
	\end{tabular}
	\caption{SV-Comp 2018 results on reducer commutativity. For space reason, we only list results of tool with better performance in these examples, which includes top three tools in the overall ranking and the reachability safety category.}
	\label{tab:svcomp}
\end{table}

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{color}
\usepackage{alltt}
\usepackage{xspace}
\usepackage{multirow}
\pagestyle{plain}
\usepackage{xcolor}
\usepackage{algorithm2e}
\usepackage{tikz,pgfplots}
\usepackage{etoolbox}
\usepackage{mathtools}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{listings}
%\usepackage{adjustbox}
%\usetikzlibrary{arrows,calc}
\captionsetup{compatibility=false}
%\usepackage{a4wide}
%\usepackage[margin=40mm, top=35mm]{geometry}

@@

\begin{table}
	\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
		& \small CBMC\cite{cbmc2} 	& \small CPA-Seq\cite{cpachecker} & \small  ESBMC-kind\cite{esbmc} & \small  UAutomizer\cite{uautomizer} &\small  VeriAbs\cite{veriabs} &\small J-Recover\\
\hline
\hline
\small \textsf{rangesum}	& 0.96 	   & 30 		 & 2.2 				 &  10				 & 180       &9.9\\
\hline
\small \textsf{avg}			 &  TO      &  TO		  &  TO				 &  TO				 &  2          &10.9\\
\hline
\small \textsf{max}		    &  TO      &  TO		 &  TO				& TO				 &  7         &9.4\\
\hline
\small \textsf{sep}		     &  TO      &  TO		  &  TO				 & TO				 &  TO        &9.9\\
\hline
\small \textsf{sum}		    &  TO      &  TO		 &  TO				& TO				&  1.7       &9.9\\
\hline
	\end{tabular}
	\caption{SV-Comp 2018 results on reducer commutativity. For space reason, we only list results of tool with better performance in these examples, which includes top three tools in the overall ranking and the reachability safety category.}
	\label{tab:svcomp}
\end{table}

@@

% Optimization table
\begin{table}
	\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
		& \multicolumn{3}{c|}{\small w/o Optimization}	& \multicolumn{3}{c|}{\small Optimized} \\
\hline
		\small Lines & \small Average & \small Median & \small Timeout & \small Average & \small Median & \small Timeout \\
\hline
\hline
		50	&	11.104	&	10.446	&	0	&	10.284	&	10.193	&	0	\\
\hline                                                                              
		100	&	19.766	&	11.239	&	1	&	29.544	&	11.172	&	3	\\
\hline                                                                             
		150	&	88.741	&	17.943	&	12	&	63.931	&	13.984	&	7	\\
\hline                                                                             
		200	&	88.741	&	169.456	&	26	&	63.931	&	13.984	&	7	\\
\hline                                                                             
		250	&	232.348	&	300.000	&	43	&	175.976	&	248.998	&	30	\\
\hline
	\end{tabular}
	\caption{....}
	\label{tab:opt2}
\end{table}

% Optimization compare graph
\begin{tikzpicture}
	\begin{axis}[%
			xmin=-5, xmax=320,
			ymin=-5, ymax=320,
			xlabel=Optimize,
			ylabel=w/o Optimization
			]
	\addplot[scatter,only marks,%
		scatter src=explicit symbolic, mark=x]%
		file {plot_data/optimize.data};
\draw (-100,-100) -- (400, 400);
\end{axis}
\end{tikzpicture}

% BMC table
\begin{table}
	\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
		& \multicolumn{3}{c|}{\small Optimized}	& & \multicolumn{3}{c|}{\small w/o Optimization} \\
\hline
		\small Lines/Vars & \small Average & \small Median & \small Timeout & Lines/Vars (jimple)& \small Average & \small Median & \small Timeout \\
\hline
\hline
		50/5	&	0.063	&	0.058	&	0	&	72.85/65.7	&	0.139	&	0.143	&	0	\\
\hline
		100/10	&	0.840	&	0.240	&	0	&	129.95/120.85	&	3.052	&	0.374	&	0	\\
\hline
		150/15	&	28.459	&	1.752	&	1	&	186.9/175.6	&	36.233	&	2.151	&	1	\\
\hline
		200/20	&	76.220	&	14.37	&	2	&	243.75/230.6	&	89.730	&	15.941	&	5	\\
\hline
		250/25	&	84.358	&	1.413	&	5	&	300.55/285.85	&	172.482	&	243.845	&	10	\\
\hline
	\end{tabular}
	\caption{....}
	\label{tab:opt2}
\end{table}

% BMC compare graph
\begin{tikzpicture}
	\begin{axis}[%
			xmin=-5, xmax=150,
			ymin=-5, ymax=150,
			xlabel=J-ReCoVer(s),
			ylabel=BMC(s)
			]
	\addplot[scatter,only marks,%
		scatter src=explicit symbolic, mark=x]%
		file {plot_data/bmc.data};
\draw (-100,-100) -- (400, 400);
\end{axis}
\end{tikzpicture}
